---
title: "Core v. Buffer"
author: "M. Ross Alexander"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Core vs. Buffer Summary

This document presents summary statistics for comparing metropolitan cores vs. the 10km reference region. The reference region is a developed area and should not be assumed to be pristine wilderness. Averages were computed for the full period of analysis (2001-2021).

```{r echo=F}
dat <- read.csv("C:/Users/malexander/Documents/r_files/northstar2023/1km_modis/core_v_buffer.csv")

# needing to but in a filter that a user can interact with

temp <- #filtered data


```

*City Name:* `r <paste0(temp$NAME, ", ", temp$state)>`\
*Biome*: `r <temp$biome>`\
*FEMA Region:* `r <temp$fema.region>`\

## Temperature

*Average core LST:* `r <temp$fema.region>`\
*Average reference LST:* `r <temp$fema.region>`\
*LST difference:* `r <temp$fema.region>`\

## Tree Cover

*Average core tree cover:* `r <temp$fema.region>`\
*Average reference tree cover:* `r <temp$fema.region>`\
*Tree cover difference:* `r <temp$fema.region>`\

## Non-tree Cover

*Average core non-tree cover:* `r <temp$fema.region>`\
*Average reference non-tree cover:* `r <temp$fema.region>`\
*Non-tree cover difference:* `r <temp$fema.region>`\

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
